Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2020-05-23 doc/network.tex
some tweaks

While an epidemic is ongoing, realized generation intervals until the current epidemic time can be aggregated to form a single distribution.
While realized generation intervals often cannot be observed in practice (because it is not possible to observe the exact moment at which individuals become infected), the aggregated distribution is analogous to data collected through contact tracing during an ongoing epidemic:
we typically want to try to make inference based on all available data.
These aggregated measurements are ``truncated'' because we do not know what happens after the current epidemic time.
These truncated intervals are similar to backward intervals during the exponential growth phase: there is a bias towards over-sampling shorter intervals, which are more likely to have concluded by the current epidemic time.
These observations allow us to make the following prediction: removing the truncation bias from aggregated generation intervals early in an epidemic will yield the initial forward generation-interval distribution, which is ``spatially corrected'' (i.e., contains information about the population structure) and will allow us to correctly infer the initial reproductive number from the exponential growth rate.

>>>>

While an epidemic is ongoing, realized generation intervals until the current epidemic time can be aggregated to form a single distribution.
While realized generation intervals can be difficult to measure in practice (because it is not possible to observe the exact moment at which individuals become infected), the aggregated distribution is analogous to data collected through contact tracing during an ongoing epidemic:
we typically want to try to make inference based on all available data.
These aggregated measurements are ``truncated'' because we do not know what happens after the current epidemic time.
These truncated intervals are similar to backward intervals during the exponential growth phase: there is a bias towards over-sampling shorter intervals, which are more likely to have concluded by the current epidemic time.
These observations allow us to make the following prediction: removing the truncation bias from aggregated generation intervals early in an epidemic will yield the initial forward generation-interval distribution, which is ``spatially corrected'' (i.e., contains information about the population structure) and will allow us to correctly infer the initial reproductive number from the exponential growth rate.
